DeepSphere: a graph-based spherical CNN

### 2019-11-07 main.tex
version submitted to ICLR'20
Updates from Overleaf

%\title{Which spherical CNN should you use?\\ DeepSphere V2}
\title{DeepSphere: a graph-based spherical CNN}
%\title{DeepSphere: an efficient graph-based spherical CNN}
%\title{DeepSphere, an efficient (& equivariant) graph-based spherical CNN}

\author{Michaël Defferrard, Martino Milani \& Frédérick Gusset \\
Institute of Electrical Engineering, EPFL, Lausanne, Switzerland \\
\texttt{\{michael.defferrard,martino.milani,frederick.gusset\}@epfl.ch}
\AND
Nathanaël Perraudin \\
Swiss Data Science Center (SDSC), Zurich, Switzerland \\
\texttt{nathanael.perraudin@sdsc.ethz.ch}
}

@@

\begin{abstract}
% We have to submit soon... The last sentence is a bit disconnected. Yep
Designing a convolution for a spherical neural network requires a delicate tradeoff between efficiency and rotation equivariance. % exactitude with respect to equivariance.
DeepSphere, a method based on a graph representation of the discretized sphere, strikes a controllable balance between these two desiderata.
% Say something here about isotropy?
This contribution is twofold.
First, we study both theoretically and empirically how equivariance is affected by the underlying graph with respect to the number of pixels and neighbors.
% 
Second, we evaluate DeepSphere on relevant problems.
Experiments show state-of-the-art performance and demonstrates the efficiency and flexibility of this formulation.
In particular, comparison with previous work on shape classification and climate event detection suggests that anisotropic filters are an unnecessary price to pay. 
%Say something about speed here... Not sure what?
% memory, computations, implementation complexity
\end{abstract}

@@

\paragraph{Theoretical convergence.}
We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme.
Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area and $d_i$ the radius of the smallest ball in $\R^3$ containing $\sigma_i$. Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
\begin{theorem}
	For a sampling $\V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$ such that 
% 	the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$  
	\begin{equation*}
	 \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} T_\V f [i] =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.
	\end{equation*} 
% 	for $n\to\infty$.
	\label{theo:pointwise convergence for a regular sampling}
\end{theorem}
As a direct implication of this theorem, $\b{L}$ converges pointwisely toward the Laplace-Beltrami operator ($\Delta_{\S^2}$). This operator commutes with rotation and hence this convergence is a strong hint for equivariance.
Importantly, the proof of Theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix \ref{sec: appendix: proof of theorem} inspires us in the construction of our graph Laplacian. It is inspirational for the graph construction and for how the parameter $t$ needs to be adjusted with respect to the number of points $n$.

@@

	Assuming $f:\mathbb S^2 \rightarrow \R$ is Lipschitz with Lipschitz constant $C_f$, we have
	\begin{equation*}
	\left| \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right| \leq C_fd^{(n)}\frac{1}{n},	    
	\end{equation*}
	where $\sigma_i\subset \S^2$ is the subset of the sphere corresponding to the patch arround $x_i$. Remember that the sampling is equal area.
	Hence, using the triangular inequality and summing all the contributions of the $n$ patches, we obtain
	\begin{equation*}
	\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right| \leq \sum_i \left| \frac{1}{4\pi^2} \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right|\leq n  C_fd^{(n)}\frac{1}{n} = C_fd^{(n)}
	\end{equation*}
	A direct application of this result leads to the following pointwise convergences
	\begin{equation*}
	\forall f \text{ Lipschiz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{\|x_i-y\|^2}{4t}}\rightarrow   \int e^{-\frac{\|x-y\|^2}{4t}}d\mu(x) 
	\end{equation*}
    \begin{equation*}
    \forall f \text{ Lipschiz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}f(x_i)\rightarrow   \int e^{-\frac{\|x-y\|^2}{4t}}f(x)d\mu(x)        
    \end{equation*}
	Definitions \ref{eq:Heat Kernel Graph Laplacian operator} and \ref{eq:Functional approximation to the Laplace-Beltrami operator} end the proof.
\end{proof}

@@

	C_{\phi^t_y} &= \|\partial_x\phi^t(\cdot;y)|\_\infty\\&

@@

$n^\alpha t^{5/2}=n^{5/2\beta+\alpha}\xrightarrow{n \to \infty} \infty$ since $\frac{5}{2}\beta+\alpha>0 \iff \beta>-\frac{2\alpha}{5}$\\

>>>>

%\title{Which spherical CNN should you use?\\ DeepSphere V2}
\title{DeepSphere: a graph-based spherical CNN}
%\title{DeepSphere: an efficient graph-based spherical CNN}
%\title{DeepSphere, an efficient (& equivariant) graph-based spherical CNN}
\author{Michaël Defferrard, Martino Milani \& Frédérick Gusset \\
Institute of Electrical Engineering, EPFL, Lausanne, Switzerland \\
\texttt{\{michael.defferrard,martino.milani,frederick.gusset\}@epfl.ch}
\AND
Nathanaël Perraudin \\
Swiss Data Science Center (SDSC), Zurich, Switzerland \\
\texttt{nathanael.perraudin@sdsc.ethz.ch}
}

@@

\begin{abstract}
% We have to submit soon... The last sentence is a bit disconnected. Yep, better... Let submit... It is time.... Submit Submit Submit Submit 2 minutes... DONE!!!!! 
Designing a convolution for a spherical neural network requires a delicate tradeoff between efficiency and rotation equivariance.
% exactitude with respect to equivariance.
DeepSphere, a method based on a graph representation of the discretized sphere, strikes a controllable balance between these two desiderata.
% Say something here about isotropy?
This contribution is twofold.
First, we study both theoretically and empirically how equivariance is affected by the underlying graph with respect to the number of pixels and neighbors.
Second, we evaluate DeepSphere on relevant problems.
Experiments show state-of-the-art performance and demonstrates the efficiency and flexibility of this formulation.
Perhaps surprisingly, comparison with previous work suggests that anisotropic filters might be an unnecessary price to pay.
%Say something about speed here... Not sure what?
% memory, computations, implementation complexity
\end{abstract}

@@

\paragraph{Theoretical convergence.}
We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme.
Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area and $d_i$ the radius of the smallest ball in $\R^3$ containing $\sigma_i$. Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
\begin{theorem}
	For a sampling $\V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$ such that 
% 	the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$  
	\begin{equation*}
	 \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} T_\V f [i] =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.
	\end{equation*} 
% 	for $n\to\infty$.
	\label{theo:pointwise convergence for a regular sampling}
\end{theorem}
As a direct implication of this theorem, $\b{L}$ converges pointwisely toward the Laplace-Beltrami operator ($\Delta_{\S^2}$). This operator commutes with rotation and hence this convergence is a strong hint for equivariance.
Importantly, the proof of Theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix \ref{sec: appendix: proof of theorem} inspires us in the construction of our graph Laplacian. It is inspirational for the graph construction and for how the parameter $t$ needs to be adjusted with respect to the number of points $n$.

@@

	Assuming $f:\mathbb S^2 \rightarrow \R$ is Lipschitz with Lipschitz constant $C_f$, we have
	\begin{equation*}
	\left| \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right| \leq C_fd^{(n)}\frac{1}{n},	    
	\end{equation*}
	where $\sigma_i\subset \S^2$ is the subset of the sphere corresponding to the patch around $x_i$. Remember that the sampling is equal area.
	Hence, using the triangular inequality and summing all the contributions of the $n$ patches, we obtain
	\begin{equation*}
	\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right| \leq \sum_i \left| \frac{1}{4\pi^2} \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right|\leq n  C_fd^{(n)}\frac{1}{n} = C_fd^{(n)}
	\end{equation*}
	A direct application of this result leads to the following pointwise convergences
	\begin{equation*}
	\forall f \text{ Lipschitz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{\|x_i-y\|^2}{4t}}\rightarrow   \int e^{-\frac{\|x-y\|^2}{4t}}d\mu(x) 
	\end{equation*}
    \begin{equation*}
    \forall f \text{ Lipschitz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}f(x_i)\rightarrow   \int e^{-\frac{\|x-y\|^2}{4t}}f(x)d\mu(x)        
    \end{equation*}
	Definitions \ref{eq:Heat Kernel Graph Laplacian operator} and \ref{eq:Functional approximation to the Laplace-Beltrami operator} end the proof.
\end{proof}

@@

	C_{\phi^t_y} &= \|\partial_x\phi^t(\cdot;y)\|_\infty\\&

@@

$n^alpha t^{5/2}=n^{5/2\beta+\alpha}\xrightarrow{n \to \infty} \infty$ since $\frac{5}{2}\beta+\alpha>0 \iff \beta>-\frac{2\alpha}{5}$\\
